### 2023-05-18 manuscript.tex
* manuscript.tex: Fix names.
* manuscript.tex: Fix inflection.

\ex.
\a. \(\mathit{Adjacent}(x, y) \coloneq \mathit{SameConst}(x, y) \land
\neg\mathit{SepFullFeet}(x, y)\)
\b. \(\mathit{SameConst}(x, y) \coloneq \exists z\ldotp
\mathit{Dom}(z, x) \land \mathit{Dom}(z, y)\)
\b. \(\mathit{SepFullFeet}(x, y) \coloneq \exists z, w\ldotp
z \neq w \land \mathit{FullFeet}(z, x) \land \mathit{FullFeet}(w, y)\)
\b. \(\mathit{FullFeet}(x, y) \coloneq \mathit{Feet}(x, y) \land
(\exists z\ldotp \mathit{Feet}(x, z) \land
(\mathit{prec}(y) = z \lor \mathit{succ}(y) = z))\)

\(\mathit{Dom}\) is the transitive closure of the syntactic
association relation, and \(\mathit{Feet}\) is the prosodic
association relation.  This is overcomplicated as a phonological
process, at least from our point of view.

@@

Ironically, more aggressive theoretical proposals have been proposed
that decompose segmental features into multiple terms, such as
\textcite{klv85ispetcg}, but only the autosegmental treatment of tonal
features is widely accepted.  These autosegmental proposals are all
subject to the abovementioned problem in that phonotactic constraints
are required.  In this sense, linear representations simplify the
computation by implicitly encode these constraints, revolving to our
original point.

>>>>

\ex.
\a. \(\mathit{Adjacent}(x, y) \coloneq \mathit{SameConst}(x, y) \land
\neg\mathit{SepFullFeet}(x, y)\)
\b. \(\mathit{SameConst}(x, y) \coloneq \exists z\ldotp
\mathit{Dom}(z, x) \land \mathit{Dom}(z, y)\)
\b. \(\mathit{SepFullFeet}(x, y) \coloneq \exists z, w\ldotp
z \neq w \land \mathit{FullFoot}(z, x) \land \mathit{FullFoot}(w, y)\)
\b. \(\mathit{FullFoot}(x, y) \coloneq \mathit{Foot}(x, y) \land
(\exists z\ldotp \mathit{Foot}(x, z) \land
(\mathit{pred}(y) = z \lor \mathit{succ}(y) = z))\)

\(\mathit{Dom}\) is the transitive closure of the syntactic
association relation, and \(\mathit{Foot}\) is the prosodic
association relation.  This is overcomplicated as a phonological
process, at least from our point of view.

@@

Ironically, more aggressive theoretical proposals have been proposed
that decompose segmental features into multiple terms, such as
\textcite{klv85ispetcg}, but only the autosegmental treatment of tonal
features is widely accepted.  These autosegmental proposals are all
subject to the abovementioned problem in that phonotactic constraints
are required.  In this sense, linear representations simplify the
computation by implicitly encoding these constraints, revolving to our
original point.
